hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2024-12-09 inst/manuscript/paper.Rmd
rename model_tabel arguments

smb_mod <- fit_model(temp = smallmouth$temp_C,
                     days = smallmouth$days,
                     species = "smb",
                     dev.type = "hatch")

@@

cat_mod <- fit_model(temp = catfish$temp_C,
                     days = catfish$days,
                     species = "catfish",
                     dev.type = "hatch")

@@

sturgeon_mod <- fit_model(days = sturgeon$days,
                          temp = sturgeon$temp_C,
                          species = "sturgeon",
                          dev.type = "hatch")

@@

#smallmouth bass
smb_res <- predict_phenology(data = data_sim,
                  dates = date_sim,
                  temperature = temp_sim,
                  spawn.date = "2000-07-01",
                  model = smb_mod$func)

# catfish
catfish_res <- predict_phenology(data = data_sim,
                  dates = date_sim,
                  temperature = temp_sim,
                  spawn.date = "2000-07-01",
                  model = cat_mod$func)

# sturgeon
# note that 16 C is pretty far out of range of temps for model fit, not best practice
sturgeon_res <- predict_phenology(data = data_sim,
                  dates = date_sim,
                  temperature = temp_sim,
                  spawn.date = "2000-07-01",
                  model = sturgeon_mod$func)

@@

```{r}
sockeye_hatch_mod <- model_select(
  author = "Beacham and Murray 1990", 
  species = "sockeye", 
  model = 2, 
  dev.type = "hatch"
  )
```

@@

# we care about when fish are out of gravel, so select emerge mod
bt_emerge_mod <- model_select(author = "Austin et al. 2017",
                            species = "bull trout",
                            model = "MM",
                            dev.type = "emerge")

>>>>

smb_mod <- fit_model(temp = smallmouth$temp_C,
                     days = smallmouth$days,
                     species = "smb",
                     development_type = "hatch")

@@

cat_mod <- fit_model(temp = catfish$temp_C,
                     days = catfish$days,
                     species = "catfish",
                     development_type = "hatch")

@@

sturgeon_mod <- fit_model(days = sturgeon$days,
                          temp = sturgeon$temp_C,
                          species = "sturgeon",
                          development_type = "hatch")

@@

#smallmouth bass
smb_res <- predict_phenology(data = data_sim,
                  dates = date_sim,
                  temperature = temp_sim,
                  spawn.date = "2000-07-01",
                  model = smb_mod$expression)

# catfish
catfish_res <- predict_phenology(data = data_sim,
                  dates = date_sim,
                  temperature = temp_sim,
                  spawn.date = "2000-07-01",
                  model = cat_mod$expression)

# sturgeon
# note that 16 C is pretty far out of range of temps for model fit, not best practice
sturgeon_res <- predict_phenology(data = data_sim,
                  dates = date_sim,
                  temperature = temp_sim,
                  spawn.date = "2000-07-01",
                  model = sturgeon_mod$expression)

@@

```{r}
sockeye_hatch_mod <- model_select(
  author = "Beacham and Murray 1990", 
  species = "sockeye", 
  model = 2, 
  development_type = "hatch"
  )
```

@@

# we care about when fish are out of gravel, so select emerge mod
bt_emerge_mod <- model_select(author = "Austin et al. 2017",
                            species = "bull trout",
                            model = "MM",
                            development_type = "emerge")
